### 2015-01-13 paper/Content/02research.tex
fixed merge issue
typo and citation fix

\subsection{Concepts \& Components of Android Applications}

Building \emph{Android} applications requires several core components of the \emph{Android} SDK to be used. This section gives a short overview and explanation of important components used in the implementation of the prototype created for this paper.

@@

Other common difficulties developers face lie with the \emph{maintainability} and \emph{extensibility} of their software. Given the \emph{Android} framework, its many components and classes that enable communication between these compontents, the structure often gets cluttered -- especially in larger application projects. For example, \emph{ListView}s\footnote{Component to \enquote{display a list of scrollable items}. \cite{SDKListView}} need \emph{Adapter}\footnote{Class to \enquote{bridge between AdapterView and the underlying data}. \cite{SDKAdapter}} to display their content, which in turn might use \emph{Loader}s\footnote{Component that \enquote{performs asynchronous loading of data}. \cite{SDKLoader}} and \emph{Cursor}s\footnote{Interface class providing access to results of database queries. \cite{SDKCursor}} to fetch the data to display.

>>>>

\subsection{Concepts \& Components of Android Applications}
Building \emph{Android} applications requires several core components of the \emph{Android} SDK to be used. This section gives a short overview and explanation of important components used in the implementation of the prototype created for this paper.

@@

Other common difficulties developers face lie with the \emph{maintainability} and \emph{extensibility} of their software. Given the \emph{Android} framework, its many components and classes that enable communication between these components, the structure often gets cluttered -- especially in larger application projects. For example, \emph{ListView}s\footnote{Component to \enquote{display a list of scrollable items} \cite{SDKListView}.} need \emph{Adapter}\footnote{Class to \enquote{bridge between AdapterView and the underlying data} \cite{SDKAdapter}.} to display their content, which in turn might use \emph{Loader}s\footnote{Component that \enquote{performs asynchronous loading of data} \cite{SDKLoader}.} and \emph{Cursor}s\footnote{Interface class providing access to results of database queries \cite{SDKCursor}.} to fetch the data to display.
